\documentclass{gradstudentresume}

\usepackage{hyperref}
\usepackage[natbib=true, style=apa]{biblatex}
\usepackage{enumitem}

\addbibresource{bibliography.bib}

\renewcommand{\myname}{\textbf{Barg, J.}}
\newcommand{\iveyaddress}{1255 Western Road, London ON N6G 0N1, Canada}

\begin{document}
	\begin{info}
		{Julian Barg}{Ivey Business School, \iveyaddress}{226-984-1461}{barg.julian@gmail.com}
	\end{info}

	\sectionheading{Education}	

	\grad{PhD Business Administration--Sustainability}{expected 2022}{Ivey Business School}{Canada}{Constructing and Deconstructing an Environmental Threat (tentative)}{Dr. Mark Zbaracki}
	\medspace

	\grad{Master of Management Science}{2017}{Peking University HSBC Business School}{China}{The Impact of Green Supply Chain Management on Corporate Social Responsibility}{Dr. Haifeng Huang}
	\medspace

	\undergrad{B.A. Chinese Studies/East Asian Studies}{2014}{Free University of Berlin}{Germany}{}



	\largespace
	\sectionheading{Papers in progress}
	\begin{itemize}
		\item \fullcite{Montgomery2021}
		\item \fullcite{Barg2021a}
		\item \fullcite{Barg2021b}
	\end{itemize}



	\largespace
	\sectionheading{Publications}

	\begin{itemize}
		\item \fullcite{Zbaracki2021}
		\item \fullcite{Huang2019}
		\item \fullcite{Huang2017}
	\end{itemize}



	\sectionheading{Awards \& Scholarships}
	\begin{itemize}
		\item Chisholm Graduate Scholarship in Sustainability, 2020
			\subitem \$15,000 annually for three years, awarded once every three years
		\item 2018 AoM Annual Meeting--Organizations and the Natural Environment Division Best Reviewer Award
	\end{itemize}



	\largespace
	\sectionheading{Presentations and other conference participation}

	\begin{pres}{OMT Doctoral Student Consortium}
		\item \presentation{81st Annual Meeting of the Academy of Management}{2021-08-04}{}{Virtual}
	\end{pres}

	\begin{pres}{Learning to be sustainable (?)}
		\item \presentation{Ivey PhD Research Series}{2021-03-02}{Ivey Business School}{Canada}
	\end{pres}

	\begin{pres}{A Few Spills a Year, That's Normal? Learning in the Pipeline Industry}
		\item \presentation{AOM ONE Doctoral Consortium}{2020-08-07}{80th Annual Meeting of the Academy of Management}{Virtual}
	\end{pres}

	\begin{pres}{Oil Spills and Organizational Learning}
		\item \presentation{Ivey PhD Research Series}{2020-02-14}{Ivey Business School}{Canada}
	\end{pres}

	\begin{pres}{The Trends of Corporate Social Responsibility in China}
		\item \presentation{3rd International Conference on CSR, Sustainability, Ethics \& Governance}{2016-08-02}{Cologne Business School}{Germany}
	\end{pres}

	% \noindent Other conference participation
	%
	% \begin{itemize}[noitemsep]
	% 	\item ARCS Online Seminar Series 2020
	% 	\item 13th Annual Ivey/ARCS PhD Sustainability Academy (2019)
	% 	\item Ivey Sustainability Research Conference 2019
	% 	\item 12th Annual Ivey/ARCS PhD Sustainability Academy (2018)
	% 	\item Ivey Sustainability Conference 2018
	% \end{itemize}

	\largespace
	\sectionheading{Teaching}

	\begin{desc}{Huawei: Struggling to Develop a More Sustainable Supply Network}{Jan 2020}{With Dr. Jury Gualandris}
		\item Co-authored Ivey Case Study on sustainable supply chain management in China
	\end{desc}

	\begin{desc}{Competing in and with China}{Spring 2018}{Dr. Klaus E. Meyer}
		\item Shadowed teaching prep and TA'd for the course
	\end{desc}

	\begin{desc}{CaseMate for \textit{Globally Responsible Leadership: Managing According to the UN Global Compact}}{Spring 2018}{Dr. Paul W. Beamish}
		\item \url{https://www.iveycases.com/CaseMateBookDetail.aspx?id=439}
	\end{desc}



	\largespace
	\sectionheading{Research Assistant work on grants}

	\begin{desc}{Greenwashing Gender in the Fortune 500}{Fall 2020}{Dr. A. Wren Montgomery, Dr. Erin Oldford, Dr. Alyson E. Byrne}
		\item Downloaded, merged, and transformed data from Compustat and BoardEx	
	\end{desc}

	\begin{desc}{Bridges Over Troubled Waters: Collective Community Action Around Water Resources in Post-Conflict Northern Ireland}{Fall 2019}{Dr. A. Wren Montgomery}
		\item Scraped Facebook groups
	\end{desc}

	\begin{desc}{A Dynamic Model of Misleading Corporate Environmental Communications}{Summer 2019}{Dr. A. Wren Montgomery}
		\item On SSHRC Insight Development Grand, \$49,305 awarded June 2018
		\item With Thomas Lyon of Erb Institute, University of Michigan
		\item Collected data on all applicable sustainability and organic certifications and assembled the data to allow for comparison of standards’ stringency
	\end{desc}

	\begin{desc}{The Causes, Methods and Consequences of Brownwashing}{Fall 2018}{Dr. Jennifer Robertson,  Dr. A. Wren Montgomery}
		\item On SSHRC Insight Development Grant, \$49,305 awarded June 2016
		\item With Thomas Lyon of Erb Institute, University of Michigan
		\item Scraped address and other info on (almost) all Californian wineries \& vineyard from varioud websites and assembled them into an interactive dashboard
		\item \url{https://www.jbarg.net/organic_vineyards}
	\end{desc}



	\largespace
	\sectionheading{References}

	\begin{itemize}
		\item \reference{Dr. Mark Zbaracki}{Associate Professor, General Management \& Strategy}{+1 (519) 661-4270}{Ivey Business School}{mzbaracki@ivey.ca}{Western University}{\iveyaddress}

		\item \reference{Dr. A. Wren Montgomey}{Assistant Professor, Sustainability \& General Management}{+1 (519) 850-3569}{Ivey Business School}{wmontgomery@ivey.ca}{Western University}{\iveyaddress}

		\item \reference{Dr. Lee Watkiss}{Assistant Professor, General Management \& Strategy}{+1 (519) 661-2022}{Ivey Business School}{lwatkiss@ivey.ca}{Western University}{\iveyaddress}

		\item \reference{Dr. Klaus Meyer}{Professor, International Business}{+1 (519) 661-4292}{Ivey Business School}{kmeyer@ivey.ca}{Western University}{\iveyaddress}
	\end{itemize}



	\largespace
	\sectionheading{Hard skills}

	\begin{itemize}
		\item German
		\item Chinese
		\item R
		\item Python
		\item Bash
		\item SQL
		\item Web scraping
		\item Topic modeling
		\item Neural networks
		\item Dashboards
	\end{itemize}

\end{document}